Optical nanostructures design, fabrication, and applications for solar/thermal energy conversion

### 2017-02-12 Submission_2016_source/submission.tex
Updated

\usepackage{lineno,hyperref}
\modulolinenumbers[5]
\usepackage{opex3}
\usepackage{color}
\usepackage{amsmath}
%%%%%%%%%%%%%%%%%%%%%
% REMOVE BEFORE SUBMISSION
\usepackage{amsmath,amssymb,graphicx}
\usepackage{dcolumn}%
\usepackage{array,multirow}
\usepackage{bm}%
%\usepackage{cite}
\usepackage{pstool}%
\usepackage{array}
\usepackage{xcolor}
\usepackage{subcaption,subfloat} % lets you have multiple pictures next to each other
%\usepackage{upgreek}
%\usepackage[numbers,sort&compress]{natbib}
\newcommand{\beginsupplement}{%
        \setcounter{table}{0}
        \renewcommand{\thetable}{A\arabic{table}}%
        \setcounter{figure}{0}
        \renewcommand{\thefigure}{A\arabic{figure}}%
     }
\journal{Solar Energy Materials and Solar Cells}
\bibliographystyle{elsarticle-num}

@@

\begin{keyword}
\ocis{(220.022) Optical design and fabrication; (230.023) Optical devices;  (240.024) Optics at surfaces; (240.031) Thin films; (350.605) Solar Energy; (310.662) Subwavelength structures, nanostructures.}
\end{keyword}

>>>>

\usepackage{lineno,hyperref}
\modulolinenumbers[5]
\usepackage{color}
\usepackage{amsmath}
%%%%%%%%%%%%%%%%%%%%%
% REMOVE BEFORE SUBMISSION
\usepackage{amsmath,amssymb,graphicx}
\usepackage{dcolumn}%
\usepackage{array,multirow}
\usepackage{bm}%
%\usepackage{cite}
\usepackage{pstool}%
\usepackage{array}
\usepackage{xcolor}
\usepackage{subcaption,subfloat} % lets you have multiple pictures next to each other
%\usepackage{upgreek}
%\usepackage[numbers,sort&compress]{natbib}
\newcommand{\beginsupplement}{%
        \setcounter{table}{0}
        \renewcommand{\thetable}{A\arabic{table}}%
        \setcounter{figure}{0}
        \renewcommand{\thefigure}{A\arabic{figure}}%
     }
\journal{Solar Energy}
\bibliographystyle{elsarticle-num}

@@

\begin{keyword}
\texttt{elsarticle.cls}\sep Optical design and fabrication \sep Optical Devices \sep Optics at surfaces \sep Thin Films \sep Solar Energy \sep Subwavelength structures, nanostructures
\end{keyword}

%\begin{keyword}
%\ocis{(220.022) Optical design and fabrication; (230.023) Optical devices;  (240.024) Optics at surfaces; (240.031) Thin films; (350.605) Solar Energy; (310.662) Subwavelength structures, nanostructures.}
%\end{keyword}
